Proposed Solution

### 2016-11-12 Ennan-Proposal/arch.tex
stuff

We propose to build \app, an automatic verification framework for 
software configuration files.
In particular, \app is built upon ConfigC and aims at addressing
all the limitations of ConfigC (mentioned in Sec.~\ref{sec:prelim}).
\app is capable of detecting many sophisticated 
configuration errors (\eg, ordering errors, missing entry errors,
and fine-grained value correlation errors) that existing
efforts cannot detect. 
Figure~\ref{fig-overview} presents
a typical \app verification workflow which contains three steps:
translation, learning, and checking. In this section, we briefly
describe how each step works.

\paragraph{Initial phase.}
We start with the assumption 
that we are given a number of (not necessarily correct) 
configuration files, called {\em sample dataset}, 
belonging to the same system (\eg, MySQL or Apache)
as the configuration file we want to verify (called as target
configuration file). Thus, these files (including sample set
and the target configure file) follow similar configuration patterns.
%In the following steps,
%we will exploit in a collection of learning algorithms 
%to build rules that describe a language model for the files.

\paragraph{Translator (Sec.~\ref{sec:lang}).}
The translator module first parses the input sample dataset 
(containing both configuration files and system environment
information), and then transforms them into a more structured
and typed intermediate representation, which follows
our defined language model (see Sec.~\ref{sec:lang} 
for more language model definition details).
When we infer the types of entries in a configuration file, 
the type of an entry cannot always be fully determined from 
a single value, because: 1) it is very hard to understand
the purposes of key-value entries in modern
software configuration files~\cite{xu15hey},
and 2) configuration files in the given sample dataset may contain 
many incorrect entries.
We, therefore, address this problem 
by introducing {\em probabilistic types}.
In particular, rather than giving a variable a single type, 
we assign several types over a probability distribution. 
We can later (in the learner module) use these more structured files
(represented in our defined language model) 
as a training set to determine those probabilistic types, 
thus finally learning the rules.

\begin{figure*}[tbp] \centering
\includegraphics[width=0.9\textwidth]{figs/overview}
\caption{\app's workflow. The green components represent configuration 
  files, including both sample configuration datasets and users' input
  configuration files to verify. 
  The purple components are the modules of \app.
  Because template DB is not necessarily used, we use dashed
  arrow between it and the learner.
  Red boxes are sub-modules within the checker.
  The yellow components are results generated by \app's modules.}
\label{fig-overview}
\end{figure*}

\paragraph{Learning (Sec.~\ref{sec-learn}).}
The input of the learner is a set of files that have been translated
into well-structured representations (\ie, the translator's
outputs). The learner module employs a collection of learning algorithms
to generate various rules and constraints,
potentially used to handle different types of configuration errors.
These rules and constraints are the outputs of the learner, 
and will be used by the checker to detect errors later.
Because the translator outputs probabilistically typed entries,
the learner is responsible for determining a type for each entry.

>>>>

We propose to build \app, an automatic verification framework for 
software configuration files, by exploring further the insights we 
obtained when building ConfigC. Figure~\ref{fig-overview} presents
a typical \app verification workflow which contains three steps:
translation into an intermediary representation, a specification 
learning, and checking the correctness of a given configuration file.

\begin{figure*}[htbp] \centering
\includegraphics[width=0.9\textwidth]{figs/overview}
\caption{\app's workflow. The green components represent configuration 
  files, including both sample configuration datasets and users' input
  configuration files to verify. 
  The purple components are the modules of \app.
  Because template DB is not necessarily used, we use dashed
  arrow between it and the learner.
  Red boxes are sub-modules within the checker.
  The yellow components are results generated by \app's modules.}
\label{fig-overview}
\end{figure*}

\paragraph{Learning Specifications.}
Similarly as before, we start with an assumption 
that we are given a number of 
configuration files belonging to the same system (\eg, MySQL or Apache).
Additionally, we assume that files in this data set are 
not necessarily correct, but if there are errors they appear only in some
file. We then translate that dataset into a more structured
and typed intermediate representation, which follows
our defined language model (cf. Sec.~\ref{sec:lang}).
Since the type of an entry cannot be fully determined from 
the entry value, we introduce {\em probabilistic types}, which is
a more flexible type notion: to a indefinite keyword it 
assigns a list of possible types together with their probability 
distribution. The learner module employs a collection of learning
 algorithms to generate various rules and constraints.
It uses type-annotated templates to infer the rules. In addition, 
there are algorithms for detecting ordering errors and missing entry
errors, which do not depend on templates. However, this time, 
since the input set is not necessarily correct, the learned rules are
also annotated with the probability indicating the likelihood of being 
correct.

potentially used to handle different types of configuration errors.
These rules and constraints are the outputs of the learner, 
and will be used by the checker to detect errors later.
Because the translator outputs probabilistically typed entries,
the learner is responsible for determining a type for each entry.
